taxadb: A High-Performance Local Taxonomic Database Interface

### 2019-04-03 paper/manuscript.Rmd
table printing

journal: "Methods in Ecology & Evolution"
date: "`r Sys.Date()`"
bibliography: refs.bib
layout: 3p
output: 
  rticles::springer_article:
    includes:
      in_header: preamble.tex
---

@@

knitr::opts_chunk$set(cache=TRUE, message=FALSE, warning=FALSE)
```

@@

```{r echo=FALSE, cache = FALSE}
status_data %>% kableExtra::kable("latex", booktabs=T) %>% 
                      kable_styling(latex_options = "striped", full_width = F)
```

```{r echo = FALSE, cache = FALSE }
trait_data %>% kableExtra::kable("latex", booktabs=T) %>% 
                      kable_styling(latex_options = "striped", full_width = F)
```

@@

```{r echo = FALSE, cache = FALSE}
joined %>% kableExtra::kable("latex", booktabs=T) %>% 
                      kable_styling(latex_options = "striped", full_width = F)
```

@@

```{r cache = FALSE, echo = FALSE}
joined %>%  
  select(elton_name, redlist_name, mass, category, id) %>%
  kableExtra::kable("latex", booktabs=T) %>% 
  kable_styling(latex_options = "striped", full_width = F)
```

>>>>

journal: "Methods in Ecology & Evolution"
date: "`r Sys.Date()`"
bibliography: refs.bib
layout: 3p
output: 
  rticles::elsevier_article:
    includes:
      in_header: preamble.tex
---

@@

printtable <- function(df){
  df %>% 
    kableExtra::kable("latex", booktabs=T) %>% 
    kable_styling(full_width = F)
}
knitr::opts_chunk$set(cache=TRUE, message=FALSE, warning=FALSE)
```

@@

```{r echo=FALSE, cache = FALSE}
status_data %>% printtable()
```

```{r echo = FALSE, cache = FALSE }
trait_data %>% printtable()
```

@@

```{r echo = FALSE, cache = FALSE}
joined %>% printtable()
```

@@

```{r cache = FALSE, echo = FALSE}
joined %>%  
  select(elton_name, redlist_name, mass, category, id) %>% printtable()
```
